Title here

### 2017-07-07 portfolio/text/ms.Rmd
More edits for reviewer response
Clearly defined risk
Add footnote
Add note about modeling risk in the methods

Diversification may benefit commercial fishers, given the extreme economic risk
that some individuals experience, particularly relative to terrestrial
agriculture [@sethi2012b]. The majority of risk insurance programs available to
terrestrial farmers (e.g. crop insurance programs) are not available to
commercial fishers [@kasperski2013]. However, fishers may be able to lower risk
by diversifying their fishing portfolio. They can, for example, target as many
species as allowed by a permit, own multiple permits, or diversify spatially and
fish in multiple regions.

The effectiveness of these diversification strategies
for increasing revenue and reducing revenue variability remains uncertain.
Theory and empirical studies demonstrate that there can be substantial
benefits to specialization for both farmers and fishers [@smith1986;
@abdulai2000; @arnason2005]. Furthermore, the majority of research examining the
effects of diversification on revenue do so at aggregate levels that combine
individuals (e.g. counties or communities; [@kasperski2013;
@sethi2014; @cline2017]). Thus, key uncertainties remain about the relationship
among diversity, fishing revenue, and fishing revenue variability at the level
of the individual.

@@

Using a unique dataset collected over 30 years on individual fishers, rather
than fleets or vessels, we examine how revenue and revenue variability of
individuals is affected by diversification. By tracking individuals, it is
possible to track people that switch fishery permits over time or use multiple
vessels and differentiate fishers that share the same vessel. We develop
a hierarchical variance-function regression model [@davidian1987; @hall1989] to
simultaneously understand the effect of species
diversity within fisheries catches on individual revenue and revenue variability.
Our model builds on results from vessel [@kasperski2013], fleet [@sethi2012b],
and community-level [@sethi2014; @cline2017] variability,
and although we model revenue *variability*, we herein equate revenue
variability with risk for consistency with Kasperski and Holland [@kasperski2013].
We simultaneously estimate the effect of species
diversity (the inverse of Simpson's diversity index [@simpson1949; @jost2006])
on individual revenue and revenue variability, and estimate effects both within
and across fishing strategies while controlling for fishing effort and latent
time effects (e.g. changing environmental conditions).
We use the model to evaluate two axes by which fishers in Alaska can
diversify fishing activities:
(1) choice of permit strategy (i.e., permit or set of permits fished), and (2)
choice of what species to fish *within* a permit strategy. To our knowledge,
this is the first application of this type of model in any natural resource
field.

@@

\label{fig:across}
\end{center}
\end{figure}
<!-- TODO AB: To me it is more intuitive that the darker, hotter colors would
represent higher values. Consdier reversing the color scale to go from red
(highest # of permit holders) to yellow (lowest #).  -->

@@

\caption{Diversifying permits reduces risk and usually increases revenue. Two
examples of expected revenue variability and median revenue for owners of (A)
individual halibut and (B) gillnet herring roe permits (dark blue) compared with
owners of the same permit plus one more (medium blue) or two more (light
blue) permits. On the y-axis, dots and lines represent posterior median and 95\%
credible intervals of expected standard deviations of year-to-year revenue rates
of return. Angled lines connects permit sets that differ by one permit.}

>>>>

Diversification may benefit commercial fishers, given the extreme economic risk
that some individuals experience, particularly relative to terrestrial
agriculture [@sethi2012b]. The majority of risk insurance programs available to
terrestrial farmers (e.g. crop insurance programs) are not available to
commercial fishers [@kasperski2013]. However, fishers may be able to lower risk
by diversifying their fishing portfolio. They can, for example, target as many
species as allowed by a permit, own multiple permits, or diversify spatially and
fish in multiple regions.
The effectiveness of these diversification strategies
for increasing revenue and reducing revenue variability remains uncertain.
Theory and empirical studies demonstrate that there can be substantial
benefits to specialization for both farmers and fishers [@smith1986;
@abdulai2000; @arnason2005]. Furthermore, the majority of research examining the
effects of diversification on revenue do so at aggregate levels that combine
individuals (e.g. counties or communities; [@kasperski2013;
@sethi2014; @cline2017]). Thus, key uncertainties remain about the relationship
among diversity, fishing revenue, and fishing revenue variability at the level
of the individual.

@@

Using a unique dataset collected over 30 years on individual fishers, rather
than fleets or vessels, we examine how revenue and revenue variability of
individuals is affected by diversification. By tracking individuals, it is
possible to track people that switch fishery permits over time or use multiple
vessels and differentiate fishers that share the same vessel.
To simultaneously understand the effect of species
diversity within fisheries catches on individual revenue and revenue variability,
we develop a hierarchical variance-function regression model [@davidian1987; @hall1989].
Our model builds on results from vessel [@kasperski2013], fleet [@sethi2012b],
and community-level [@sethi2014; @cline2017] variability,
and, although we model revenue variability, we herein equate revenue
variability with financial risk for consistency 
with Kasperski and Holland [@kasperski2013][^2].
We simultaneously estimate the effect of species
diversity (the inverse of Simpson's diversity index [@simpson1949; @jost2006])
on individual revenue and revenue variability, and estimate effects both within
and across fishing strategies while controlling for fishing effort and latent
time effects (e.g. changing environmental conditions).
We use the model to evaluate two axes by which fishers in Alaska can
diversify fishing activities:
(1) choice of permit strategy (i.e., permit or set of permits fished), and (2)
choice of what species to fish *within* a permit strategy. To our knowledge,
this is the first application of this type of model in any natural resource
field.

[^2]: More specifically, variability is one component of risk. Risk combines
elements of variability, uncertainty, and loss to define the "possibility of
a bad thing happening" [@sethi2010b].

@@

\label{fig:across}
\end{center}
\end{figure}

@@

\caption{Diversifying permits reduces revenue variability and usually increases revenue. Two
examples of expected revenue variability and median revenue for owners of (A)
individual halibut and (B) gillnet herring roe permits (dark blue) compared with
owners of the same permit plus one more (medium blue) or two more (light
blue) permits. On the y-axis, dots and lines represent posterior median and 95\%
credible intervals of expected standard deviations of year-to-year revenue rates
of return. Angled lines connects permit sets that differ by one permit.}
